I cannot begin to express my thanks to my wife, Jennifer Gahee Kim,
who sincerely supports me with love, wisdom, insight, and delicious foods.
It is very special to share my life with someone who is not just my wonderful
wife, but also the greatest friend a person could ever have.
You make my life happier than ever.

I also want to thank my mother Jiwon and my father Sangsoo for guiding me
throughout my life.
I would not have been able to find, start, and finish the graduate school without
their unconditional love and support.

I am also grateful to my brother Jihoon, his family Eunchae and Dongkwon,
and parents-in-law Eungyoung Lee and Boogyun Kim for encouraging me to pursuit
my degree.
Especially, my brother has been a great tutor who teaches me
how to add numbers, how to program, how to solve puzzles, and many more
in the most interesting ways.

I want to thank the members of my committee: Greg Turk, Jarek Rossignac,
Jun Ueda, Katsu Yamane, and my advisor C. Karen Liu.
Each of you encouraged and help me to become a much stronger and solid
researcher with insightful suggestions on my research direction and
communication skills.

I would like to extend my sincere thanks to my lab-mates
who have shared invaluable discussions during the entire program:
Kihwan Kim, Chirs Wojtan, Jason Williams, Yuting Ye, Sumit Jain,
Jihun Yu, Tina Zhou, Jie Tan, Yuting Gu, Chen Tang, Karthik Raveendran, 
Mark Luffel, Topraj Gurung, Yunfei Bai, Kristin Siu, Yunseong Song,
Jeongseok Lee, John Turner, Alex Clegg, Wenhao Yu, and many more.
In addition, I would like to thank my friends/mentors: Yeongjin, Seongmin,
Jaesik, Yeongseok, Donggu, Byoungyoung, and Taesoo.
I am really sorry if I forgot anyone.

I wish to particularly thank Evan Kanso, Jovan Popovi\'{c}, Jim McCann, and
Katsu Yamane, who provided me with encouragement and patience throughout the
duration of my internships: all the experiences widen my research horizons.

Special thanks to my mentors, Wangjae Lee and Jaehong Kim, who
guides my life to the better direction.

I would like to express my deepest appreciation to my advisor, C. Karen Liu.
I feel extremely fortunate to have her as my advisor.
Her intellectual insights and creativity to research problems was a great
source of inspiration which carves me as a better researcher.
Her enthusiasm of research encourages me to keep working on more challenging
problems, which is one of the most valuable lessons learned in my life.
It was a great honor to be under her supervision for the last six years.
I will miss all interactions with you, Karen, 
including both insightful discussions and fun jokes. 












