\documentclass[12pt]{gatech-thesis}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,color,subfigure,soul}
\usepackage{sidecap}
\usepackage{lscape}
\usepackage{wrapfig}
\usepackage{hhline}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{algorithmic}
\include{defs}
\usepackage{array}

%%
%% This example is adapted from ucthesis.tex, a part of the
%% UCTHESIS class package...
%%
\title{Developing Agile Motor Skills \protect\\
  on Virtual and Real Humanoids} 
%% If you want to specify a linebreak
                               %% in the thesis title, you MUST use
                               %% \protect\\ instead of \\, as \\ is a
                               %% fragile command that \MakeUpperCase
                               %% will break!
\author{Sehoon Ha}
\department{School of Interactive Computing}

%% Can have up to six readers, plus principaladvisor and
%% committeechair. All have the form
%%
%%  \reader{Name}[Department][Institution]
%%
%% The second and third arguments are optional, but if you wish to
%% supply the third, you must supply the second. Department defaults
%% to the department defined above and Institution defaults to Georgia
%% Institute of Technology.

\principaladvisor{Dr. C. Karen Liu}
\firstreader{Dr. Greg Turk}
\secondreader{Dr. Jarek Rossignac}
\thirdreader{Dr. Jun Ueda}[School of Mechanical Engineering]
\fourthreader{Dr. Katsu Yamane}[Disney Research Pittsburgh][]
\degree{Doctor of Philosophy}

%% Set \listmajortrue below, then uncomment and set this for
%% interdisciplinary PhD programs so that the title page says
%% ``[degree] in [major]'' and puts the department at the bottom of
%% the page, rather than saying ``[degree] in the [department]''

%% \major{Algorithms, Combinatorics, and Optimization} 

\copyrightyear{2015}
\submitdate{December 2015} % Must be the month and year of graduation,
                         % not thesis approval! As of 2010, this means
                         % this text must be May, August, or December
                         % followed by the year.

%% The date the last committee member signs the thesis form. Printed
%% on the approval page.
\approveddate{31 July 2015}

%% \bibfiles{example-thesis}
\bibfiles{thesis}

%% The following are the defaults
%%    \titlepagetrue
%%    \signaturepagetrue
%%    \copyrightfalse
%%    \figurespagetrue
%%    \tablespagetrue
%%    \contentspagetrue
%%    \dedicationheadingfalse
%%    \bibpagetrue
%%    \thesisproposalfalse
%%    \strictmarginstrue
%%    \dissertationfalse
%%    \listmajorfalse
%%    \multivolumefalse

\begin{document}
\bibliographystyle{gatech-thesis}
%%
\begin{preliminary}
\begin{dedication}
\null\vfil
{\large
\begin{center}
To my parents, \\\vspace{12pt}
Sangsoo Ha and Jiwon Lee, \\\vspace{12pt}
who have given me the best love and support \\\vspace{12pt}
throughout my life.
% To myself,\\\vspace{12pt}
% Sehoon Ha,\\\vspace{12pt}
% the only person worthy of my company.
\end{center}}
\vfil\null
\end{dedication}
%% \begin{preface}
%% Theses have elements.  Isn't that nice?
%% \end{preface}
\begin{acknowledgements}
\input{acknowledgements}
\end{acknowledgements}
% print table of contents, figures and tables here.
\contents
% if you need a "List of Symbols or Abbreviations" look into
% gatech-thesis-gloss.sty.
\begin{summary}
\input{summary}
\end{summary}
\end{preliminary}
%%

%% \input{introduction}
\input{intro2}
\input{related}
\input{landing/chapter}
\input{falling/chapter}
\input{parkour/chapter_design}
\input{parkour/chapter_cmac}
\input{optskills/chapter}
\input{learning/chapter}
\input{conclusion}

% \nocite{*}
%% We need this since this file doesn't ACTUALLY \cite anything...
%%
%% \appendix
%% \chapter{Some Ancillary Stuff}

%% Ancillary material should be put in appendices, which 
%% appear just before the bibliography. 

\begin{postliminary}
\references
%% \postfacesection{Index}{%
%% %%             ... generate an index here
%% %%         look into gatech-thesis-index.sty
%% }

\begin{vita}
  \input{vita}
\end{vita}
\end{postliminary}

\begin{abstract}
Demonstrating strength and agility on virtual and real humanoids has
been an important goal in computer graphics and robotics.
However, developing physics-based controllers for various agile motor skills
requires a tremendous amount of prior knowledge and manual labor due to
complex mechanisms of the motor skills.
The focus of the dissertation is to develop a set of computational tools to
expedite the design process of physics-based controllers that can execute a
variety of agile motor skills on virtual and real humanoids.
Instead of designing directly controllers real humanoids, this
dissertation takes an approach that develops appropriate theories and models in
virtual simulation and systematically transfers the solutions to hardware systems.

The algorithms and frameworks in this dissertation span various topics from
specific physics-based controllers to general learning frameworks.
We first present an online algorithm for controlling falling and landing
motions of virtual characters.
The proposed algorithm is effective and efficient enough to generate falling
motions for a wide range of arbitrary initial conditions in real-time.
Next, we present a robust falling strategy for real humanoids that can manage
a wide range of perturbations by planning the optimal contact sequences.
We then introduce an iterative learning framework to easily design
various agile motions, which is inspired by human learning techniques.
The proposed framework is followed by novel algorithms to
efficiently optimize control parameters for the target tasks, especially when
they have many constraints or parameterized goals.
Finally, we introduce an iterative approach for exporting simulation-optimized
control policies to hardware of robots to reduce the number of hardware
experiments, that accompany expensive costs and labors.
\end{abstract}

\end{document}
